---
title: "Load Spatial data"
date: "`r format(Sys.time(), '%d %m %Y')`"
format:
  html:
    embed-resources: true
    code-fold: show
params:
  fig.path: "./Figures/00/"
editor_options: 
  chunk_output_type: console
---

```{r background-job, eval=FALSE, include=FALSE}
source("../bin/render_with_jobs.R")

# quarto
# render_html_with_job(out_dir = lab_dir)
# fs::file_move(path = file, new_path = paste0(lab_dir, file))

# currently using quarto for github and kniter for html due to source code option 
render_git_with_job(fig_path = "./Figures/00/")
# Changes the figure path from ./Figures/ to ../Figures/:
system2(command = "sed", stdout = TRUE,
        args = c("-i", "''","-e", 's/src=\\"\\./src=\\"\\.\\./g',
                 paste0("./md_files/", basename("./00_load_st_data.md"))))

# kniter
knit_html_with_job(out_dir = "../lab_book/00_load_st_data/", fig_path = "./Figures/00/")
```

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.width   = 6.6929133858,
  fig.path    = params$fig.path,#"../Figures/",
  fig.align   = "center",
  message     = FALSE,
  warning     = FALSE,
  dev         = c("png"),
  dpi         = 300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename,
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
  })

select <- dplyr::select
# setwd('~/work/Brolidens_work/Projects/Spatial_Microbiota/src')
```

### Load libraries
```{r Load-libraries, message=FALSE, warning=FALSE}
##################
# LOAD LIBRARIES #
##################
library(tidyverse)
library(tidyseurat)
library(Seurat)
# remotes::install_version("Seurat", "4.4.0", repos = c("https://satijalab.r-universe.dev", getOption("repos")))
library(hdf5r)

library(xml2) # loads the image 
library(sp)
library(terra)
library(cowplot)

source("../bin/help_functions.R")
source("../bin/spatial_visualization.R")

#################
# COLOR PALETTS #
#################
pal <- rep(c(RColorBrewer::brewer.pal(9,"Set1"),
         RColorBrewer::brewer.pal(9,"Pastel1"),
         RColorBrewer::brewer.pal(8,"Accent"),
         RColorBrewer::brewer.pal(8,"Set2"),
         RColorBrewer::brewer.pal(8,"Pastel2") ,
         scales::hue_pal()(8)),99)

```

some of the original images has dimentions less than 2000px x 2000 px, this creates some limitations when plotting all the images together, because you have to use the smallest width and height as limits in order to not get a out of range error.

to mitigate this I have extended the images so that all have dimensions of 2000px x 2000 px. When doing this it is important that you only add extra space to the right and bottom side of the image, otherwise the coordinates of the spots will be wrong, also you need to add a fill for the "new portion", for the crop_img function to work.

### Load Visium data
```{r Load-data}
#########
# PATHS #
#########
m_path <- "https://www.ncbi.nlm.nih.gov/geo/download/?acc=GSE217237&format=file&file=GSE217237%5Fmetadata%2Ecsv%2Egz"
input_dir <- "../data/spatial_data"
result_dir <- "../results/00_load_st_data/"
if( isFALSE(dir.exists(result_dir)) ) { dir.create(result_dir,recursive = TRUE) }

#############
# LODA DATA #
#############
download.file(m_path, destfile = "../data/metadata.csv.gz")
meta <- read_csv(gzfile("../data/metadata.csv.gz"))
# meta <- read_csv("../data/ST-samples_metadata.csv")

h5_files <- list.dirs(path = input_dir,
                      full.names = T, recursive = T) %>%
            grep("P\\d\\d\\d$", ., value = TRUE) %>%
            set_names(., str_extract(., "P\\d\\d\\d$"))
sample_id <- c("P020", "P045", "P050", "P057",
               "P008", "P031", "P080", "P044", "P026", "P105", 
               "P001", "P004", "P014", "P018", "P087", "P118",
               "P021", "P024", "P067", "P081", "P117" ) %>% set_names()

h5_files <- h5_files[names(h5_files) %in% sample_id]
# the new version of seurat v5 does not allow to read in any other than low res img
# to circumvent this rename the hires to low res and move the lowres file
image <- map(h5_files, 
             ~Read10X_Image(
               filter.matrix = T,
               image.dir = paste0(.x, "/spatial"),
               image.name = "tissue_hires_image.png"))

# Read in h5 files and create Seurat Object
seuratObj_list <- pmap(list(h5_files, image, names(h5_files)),
                       ~Load10X_Spatial(
                         filename = "filtered_feature_bc_matrix.h5",
                         filter.matrix = T,
                         assay = "RNA",
                         data.dir = ..1,
                         image =  ..2,
                         slice = ..3)) 
rm(image)
# sample_id <- names(h5_files) %>% set_names()
```

### Tidy up the seurat object
```{r Clean-SeuratObj}
####################################
# RENAME SAMPLES, SPOTS AND IMAGES #
####################################
seuratObj_list <- seuratObj_list %>%
  imap(., ~AddMetaData(object = .x, 
                       metadata = rep(.y, length(Idents(.x))), 
                       col.name = "orig.ident")) %>%
  map(.,  ~SetIdent(., value = .@meta.data$orig.ident)) %>%
  imap(., ~RenameCells(.x, 
                      new.names = paste0(.y,"_", gsub("-.*","",colnames(.x[["RNA"]])))) ) %>%
  imap(., ~ {.x@images <- set_names(.@images,.y); .x})

##################
# MERGE SAMPLES #
#################
# Merge datasets into one single seurat object

DATA  <- merge(seuratObj_list[[1]], y = seuratObj_list[2:length(seuratObj_list)])
# DATA <- JoinLayers(DATA) # Seurat version 5.0
rm(seuratObj_list)
```

```{r Manual-annot}
##########################
# ADD MANUAL ANNOTATION #
#########################
### Load morphology annotation
a2 <- map(sample_id, ~xml2::as_list( read_xml( paste0( input_dir,"/",.x,"/",.x,".svg")) ) )
dd <- map(a2, ~as.numeric( strsplit( attributes(.x$svg)$viewBox , " ")[[1]] ))
dd2 <- map(sample_id, ~dim(DATA@images[[.x]]@image))

# sample_id <- "P097"
# a2 <- a2[["P097"]]
# dd <- dd[["P097"]]
# dd2 <- dd2[["P097"]]

# add image coordinates to the seurat object
get_img_coord <- function(DATA, sample_id){
  img_coord <- DATA@images[[sample_id]]@coordinates
  DATA@images[[sample_id]]@coordinates <<- img_coord 
}

# add manual spatial annotation
get_sp_annot <- function(a2, dd, dd2, sample_id){
  scale.factor <- DATA@images[[sample_id]]@scale.factors$hires
  img_coord <- DATA@images[[sample_id]]@coordinates
  
  id <- a2$svg %>%
    map_chr(., ~attr(.x,"id")) %>% 
    set_names(seq_along(.), .)
  
  annot_coord <- id %>%
    map(., ~get_shape(a2$svg[[.x]]) ) %>%
    map(., ~as_tibble(.x, .name_repair="unique"))  %>%
    # convert the view box from the svg to the pixel dimensions of the raster img:
    map(., ~mutate(.x, x = .x[[1]]*dd2[2]/dd[3],
                       y = .x[[2]]*dd2[1]/dd[4] )) %>%
    map(., ~rowid_to_column(., var = "path_idx")) %>%
    {. ->>  temp} %>%
    bind_rows(., .id="name") %>%
    group_by(., name) %>%
    mutate(elem_idx = cur_group_id()) %>% # group_indices(., name)
    ungroup() %>%
    mutate(colour = ifelse(grepl("fov|zoom|full_image",.$name),
                           "transparent", "black")) %>%
    list(.) %>%
    set_names(., sample_id[1])
  
  DATA@tools <<- append(DATA@tools, annot_coord )
  
  img_coord <- temp %>%
    list_modify("fov" = NULL, "full_image" = NULL, "zoom" = NULL) %>%
    compact() %>%
    imap(., ~mutate(img_coord, !!.y := sp::point.in.polygon(
         point.x = img_coord$imagecol*scale.factor,
         point.y = img_coord$imagerow*scale.factor,
         pol.x = .x$x,
         pol.y = .x$y )) ) %>%
    map(., ~select(.x, last_col())) %>%
    cbind(img_coord, .)
  
  DATA@images[[sample_id]]@coordinates <<- img_coord 
  
  sp_annot <- img_coord %>%
    rownames_to_column(., var = "barcodes") %>%
    mutate(across(7:ncol(.), ~ifelse(. == 0, NA, .)) ) %>%
    pivot_longer(., cols = 7:ncol(.), names_to ="sp_annot", values_to = "count") %>%
    filter(!(is.na(count))) %>%
    group_by(barcodes) %>%
    mutate(dupp = row_number()) %>%
    ungroup() %>%
    filter(., .$dupp == 1) %>%
    select(., barcodes, sp_annot)
  
  #DATA <<- left_join( DATA, sp_annot, by=c(".cell"="barcodes", "sp_annot"="sp_annot")) 
  
  return(list(coord=annot_coord, annot=sp_annot))
}
annot <- list(a2, dd, dd2, names(a2)) %>%
  pmap(., ~get_sp_annot(..1, ..2, ..3, ..4)) %>%
  set_names(., names(a2))

sp <- map(annot, 2) %>% bind_rows()

DATA <-  DATA %>%
  left_join(., sp, by=c(".cell"="barcodes")) %>%
  mutate(sp_annot2 = .$sp_annot) %>%
  mutate(sp_annot = case_match(
    sp_annot2,
    c("epi_1","epi_2", "epi_3", "epi_4") ~ "epi",
    c("SubMuc_2", "SubMuc_3", "SubMuc_4") ~ "SubMuc",
    c("fov_centered","fov") ~ NA, .default = sp_annot2), .before = "orig.ident" ) %>%
  # mutate(sp_annot = ifelse(grepl("epi", .$sp_annot2), "epi", 
  #                          ifelse(grepl("SubMuc", .$sp_annot2), "SubMuc", .$sp_annot2 ))) %>%
  select(-sp_annot2)

DATA
```

```{r crop-img}
# adds a matrix with zeros outside the polygon boundary to DATA@misc$alpha
# when plotting it is added as a 4th dim to the image matrix  
# to specify alpha for each pixel in the image
mask_background.fun <- function(df, im, sampleid, manual = TRUE){
  # get polygon coordinates for individual polygons:
  df <- df %>%
    select( any_of(c("name","path_idx", "x", "y"))) %>% 
    filter(grepl("epi|SubMuc", .$name)) %>% 
    split(~name) 
  
  # Function to create SpatialPolygons from a dataframe
  createSpatialPolygons <- function(df) {
    # Convert dataframe to SpatialPointsDataFrame
    #coordinates(df) <- c("y","x")
    coordinates(df) <- c("x", "y")
    
    # Order the points based on 'path_idx'
    df <- df[order(df$path_idx, decreasing = F), ]
    #df <- df %>% arrange(desc(path_idx))
    
    # Create a SpatialPolygons object
    poly <- SpatialPolygons(list(Polygons(list(Polygon(df)), ID = df$name[1])))
    
    return(poly)
  }
  
  # Apply the function to each element of the list
  polygons_list <- map(df, ~createSpatialPolygons(.x))
  
  # Combine the SpatialPolygons into a single object
  combined_polygon <- do.call("rbind", polygons_list)
  
  # Convert it to a polygon (SpatVector)
  polygon <- vect(combined_polygon)
  
  # get image matrix and convert to rgb before rasterizing
  img <- matrix(
      rgb(im[,,1],im[,,2],im[,,3], im[4,,]* 1), nrow=dim(im)[1])
  raster <- rast(img)
  
  rasterized <- rasterize(polygon, raster)
  rasterized <- flip(rasterized, direction="vertical")
  
  # Plot the polygon
  # plot(polygon)

  # Crop the raster using the polygon
  cropped_raster <- mask(raster, rasterized, updatevalue=0)
  
  # Plot the cropped raster to verify
  # plot(cropped_raster)

  cropped_raster <- ifel(cropped_raster > 0, 1, cropped_raster)
  
  image_array <- as.array(cropped_raster)[,,1] # keep first dim only 
  #NA_idx <- which(is.na(image_array[,,1]))
  
  # minpulate image matrix
  #im <- replace(im, list = which(image_array != 0)), values = 1)
  DATA@misc$alpha <<- append(DATA@misc$alpha, set_names(list(image_array), sampleid) )
}

walk(sample_id, ~mask_background.fun(DATA@tools[[.x]], DATA@images[[.x]]@image, .x) )
```

```{r eval=FALSE}
df_ <- DATA@images[["P031"]]@coordinates %>%
    mutate(scale_fact = DATA@images[["P031"]]@scale.factors$hires) %>%
    mutate(imagecol = .$imagecol * .$scale_fact) %>%
    mutate(imagerow = .$imagerow * .$scale_fact) %>%
  rename( y = "imagerow", x = "imagecol") %>%
  rename(flightlineID="tissue") %>% select(-row, -col, -scale_fact)

ggplot(df_, aes(x=x, y=y)) +
  #geom_point(size=3) + 
  theme_classic() +
    ggstar::geom_star(
      starshape = "hexagon",
      fill = "red",
      size = 2,
      #stroke = 0,
      alpha = 1
    )
  geom_encircle()
  stat_contour_fill(aes(z = tissue))
  geom_density_2d(data = df, aes(x=x, y=y), contour_var = "count", contour = T)
  
m = list(x=df$x, y=df$y, z=matrix(1:12, 4, 3))
  
  resx <- ( m$x[length(m$x)] - m$x[1] ) / (length(m$x)-1)
  resy <- ( m$y[length(m$y)] - m$y[1] ) / (length(m$y)-1)
    xmn <- min(m$x) - 0.5 * resx
    xmx <- max(m$x) + 0.5 * resx
    ymn <- min(m$y) - 0.5 * resy
    ymx <- max(m$y) + 0.5 * resy
  z <- t(m$z)
  z <- z[nrow(z):1, ]

las_df <- df_
  
las_df1 <- las_df[which(las_df$flightlineID == 1), ]
#las_df2 <- las_df[which(las_df$flightlineID == 2L), ]
las_vect1 <- vect(las_df1, geom = c('x', 'y'), crs = 'EPSG:32755')
#las_vect2 <- vect(las_df2, geom = c('X', 'Y'), crs = 'EPSG:32755')
las_rast <- rast(xmin=0, nrow = length(unique(las_df$x)), ncol = length(unique(las_df$y)), crs='EPSG:32755')
set.ext(las_rast, c(min(las_df$x), max(las_df$x), min(las_df$y), max(las_df$y)))
pts1_rast <- rasterize(las_vect1, las_rast, fun = length)
pts2_rast <- rasterize(las_vect2, las_rast, fun = length)
pts1_pts2_rast <- c(pts1_rast, pts2_rast)
names(pts1_pts2_rast) <- c('lyr.1', 'lyr.2') # have to attend to this as both lyr.1 after `c(`
plot(pts1_pts2_rast$lyr.1, col = 'red')

plot(pts1_rast)
bo <- boundaries(pts1_rast, inner=T, classes=T, directions=8, falseval=0,)
bo <- patches(bo, directions=8, zeroAsNA=T, allowGaps=TRUE)
plot(bo)

img <- rast("/Users/vilkal/work/Brolidens_work/Projects/Spatial_Microbiota/data/Spatial_data/P008/spatial/detected_tissue_image.jpg")
plot(img)
bo <- plotRGB(img, 3, 1, 1)
bo <- rast(bo)
bo <- boundaries(bo, inner=T, classes=T, directions=8, falseval=0,)
plot(bo)

contour(pts1_rast, filled=TRUE, nlevels=1)
raster <- contour(img, filled=TRUE, nlevels=1)
raster <- ifel(raster > 200, NA, raster)
plot(raster)

r <- contour(img, filled=TRUE, nlevels=3)
contour(img, add=TRUE)

plot(img)
lines(v)
v <- as.contour(img) %>% st_as_sf()
plot(v)
r <- rast(v)

a <- aggregate(v)

a <- as.polygons(v)
bo <- boundaries(a, inner=F, classes=T)

plot(img)
plot(r)
lines(v)

template <- disagg(rast(raster), 10)
rr <- resample(raster, template)
rr <- floor(rr/100) * 100
v <- as.polygons(rr)
plot(v, 1, col=terrain.colors(7))

cropped_raster <- mask(img, a, updatevalue=0)
```

```{r crop-by-boundary, eval=FALSE}
https://stackoverflow.com/questions/74153263/calculate-distance-of-points-to-polygon-boundary-using-terra-package-in-r
# can identify the boundary of the tissue and use it to crop
# it gives a more pixelated border than when using a hand drawn polygon as in the function
# above "mask_background.fun()"
find_boundary.fun <- function(im){
  img <- matrix(
      rgb(im[,,1],im[,,2],im[,,3], im[4,,]* 1), nrow=dim(im)[1])
  img <- rast(img)
  #plot(img)
  
  i <- im[,,1]+im[,,2]+im[,,3]
  #i <- replace(im[,,1], list = which(im[,,1] > .7), values = 0)
  
  #raster <- rast(im[,,1])
  raster <- rast(i)
  # plot(raster)
  raster <- ifel(raster > 2.9, NA, raster)
  contour(raster, filled=TRUE, nlevels=5)
  r <- sieve(raster, directions=8, threshold=500)
  # plot(r)
  
  rc2 <- classify(r, matrix(c(0, NA,
                              2, 1,
                              3, 1), ncol=2, byrow=TRUE), 
                  include.lowest=TRUE, brackets=F)
  plot(rc2)
  
  # Extract only the boundary
  bo <- boundaries(rc2, inner=F, classes=T)
  # plot(bo)
  
  # Convert SpatRaster to SpatialPolygonsDataFrame
  boundary_polygon <- as.polygons(bo) 
  # plot(boundary_polygon)
  
  # Crop the raster using the polygon
  cropped_raster <- mask(img, boundary_polygon, updatevalue=0)
  plot(cropped_raster)
  
  return(boundary_polygon)
}

crop_with_poly.fun <-(im, polygon) {
  # get image matrix and convert to rgb before rasterizing
  img <- matrix(
      rgb(im[,,1],im[,,2],im[,,3], im[4,,]* 1), nrow=dim(im)[1])
  raster <- rast(img)
  
  rasterized <- rasterize(polygon, raster)
  rasterized <- flip(rasterized, direction="vertical")
  
  # Plot the polygon
  # plot(polygon)

  # Crop the raster using the polygon
  cropped_raster <- mask(raster, rasterized, updatevalue=0)
  
  # Plot the cropped raster to verify
  # plot(cropped_raster)

  cropped_raster <- ifel(cropped_raster > 0, 1, cropped_raster)
  
  image_array <- as.array(cropped_raster)[,,1] # keep first dim only 
  #NA_idx <- which(is.na(image_array[,,1]))
  
  # minpulate image matrix
  #im <- replace(im, list = which(image_array != 0)), values = 1)
  DATA@misc$alpha <<- append(DATA@misc$alpha, set_names(list(image_array), sampleid) )
}

#boundary_polygon <- find_boundary.fun(DATA@images[["P057"]]@image)
boundary_polygon <- map(sample_id, ~find_boundary.fun(DATA@images[[.x]]@image))
walk(sample_id, ~crop_with_poly.fun(DATA@images[[.x]]@image, .x) )

# im <- DATA@images[["P081"]]@image

```

### Add meta data
```{r add-groups}
meta <- meta %>%
  select(orig.ident="ID", groups=contains("Luminal_gr"), Tissue_gr=contains("Tissue_gr")) %>%
  filter(orig.ident %in% sample_id)

DATA <-  DATA %>%
  left_join(., meta, by="orig.ident") %>%
  select(groups, Tissue_gr, sp_annot, everything())
  
```

```{r 00a_plot_img, fig.height=12.5, fig.width=12.5}
# dev.new(height=12.5, width=12.5, noRStudioGD = TRUE)
DATA %>%
  filter(!(is.na(.$sp_annot))) %>%
  plot_spatial.fun(., 
        sampleid = sample_id,
        sp_annot = F,
        lab = T,
        save_space = F,
        alpha = 0, # hides the spots
        geneid = "nFeature_RNA",
        zoom = NULL,
        ncol = 5,
        img_alpha = 1) + theme(legend.position = "none") # theme_nothing() #

```

```{r test, fig.height=14, fig.width=6, eval=FALSE}
# dev.new(height=4.5, width=5, noRStudioGD = TRUE)
# dev.new(height=2*5, width=2*4, noRStudioGD = TRUE)
(p <- plot_spatial.fun(DATA, 
      sampleid = sample_id,
      sp_annot = T, 
      lab = T,
      save_space = T,
      alpha = 1,
      geneid = "nFeature_RNA",
      zoom = "zoom",
      ncol = 4,
      annot_line = .2,
      point_size = .3,
      img_alpha = 0) +  theme(legend.position = "none")) 

ggsave("./fig_1_.pdf", p)
library(directlabels)
# dev.new(height=2*5, width=2*4, noRStudioGD = TRUE)
p <- DATA %>%
  plot_st_meta.fun(.,  
          assay="RNA",
          feat = "sp_annot",
          zoom = "full_image",
          ncol = 5,
          annot_line = .1,
          annot_col = "black",
          img_alpha = 0,
          point_size = 0.7
        )
```

NB! The zoom setting is now cutting off som of the largest samples (P020 and P057)
When plotting these samples use the fov_centered

### Cluster resolutions on tissue
```{r 00_plot_annot_on_tissue, dev = c("png", "pdf")}
# dev.new(width=6.6929133858, height=14, noRStudioGD = TRUE)
plots <- DATA %>%
  mutate(id = orig.ident, gr = groups) %>%
  nest(., data = -c("gr", "id")) %>%
  arrange(gr) %>%
  mutate( "sp_annot" = pmap(., 
    ~plot_spatial.fun(..3, sampleid=..1, geneid="sp_annot", img_alpha = .5, colors = c("#FBB4AE", "#B3CDE3", "red"),
                      point_size = 0.6, annot_line = .1, zoom="fov_centered", save_space = F) + theme(legend.position="none"))) %>%
  mutate( "nFeature_RNA" = pmap(., 
    ~plot_spatial.fun(..3, sampleid=..1, geneid="nFeature_RNA",point_size = 0.6, 
                      annot_line = .1, zoom="fov_centered", save_space = F) + 
      theme(legend.position="none")))

ncols <- table(plots$gr)
combined <- split(plots, ~gr) %>%
  map(., ~plot_grid( plotlist = c(.x$sp_annot, .x$nFeature_RNA), nrow = 2, byrow = T ))
#ggsave("./fig_L1&L3.pdf", combined, width = 28, height = 5)
#ggsave("./fig_.pdf", combined, width = 5, height = 5)
```

```{r 00b_L1, fig.height=15, fig.height=5, fig.width=2.5*ncols["L1"], dev = c("png", "pdf")}
#| echo: false
# dev.new(width=2.5*ncols["L1"], height=5, noRStudioGD = TRUE)
combined[[1]]
```

```{r 00c_L2, fig.height=15, fig.height=5, fig.width=2.5*ncols["L2"], dev = c("png", "pdf")}
#| echo: false
# dev.new(width=2.5*ncols["L2"], height=5, noRStudioGD = TRUE)
combined[[2]]
```

```{r 00d_L3, fig.height=15, fig.height=5, fig.width=2.5*ncols["L3"], dev = c("png", "pdf")}
#| echo: false
# dev.new(width=2.5*ncols["L3"], height=5, noRStudioGD = TRUE)
combined[[3]]
```

```{r 00e_L4, fig.height=15, fig.height=5, fig.width=2.5*ncols["L4"], dev = c("png", "pdf")}
#| echo: false
# dev.new(width=2.5*ncols["L4"], height=5, noRStudioGD = TRUE)
combined[[4]]
```

## Plot spots to be removed
```{r 00f_plot_spots_to_remove, fig.height=1.7*6, fig.width=2*4}
# dev.new(width=2.5*5, height=2.5*5, noRStudioGD = TRUE)

DATA <-  DATA %>%
  mutate(filt = case_when(is.na(.$sp_annot)  ~ 'filt',
                          TRUE ~ 'keep')) 
DATA %>%
  plot_st_meta.fun(., 
          lvls = sample_id,
          lab = F,
          assay="RNA",
          feat = "filt",
          zoom = "zoom",
          ncol = 4,
          annot_line = .1,
          img_alpha = 0,
          point_size = .5
        )
```

### Remove NA spots
```{r remove-NA-spots}
dim(DATA)
# Filter spots outside manual annotation
DATA <- DATA[, !(is.na(DATA$sp_annot))]
DATA$filt <- NULL

dim(DATA)
DATA
```

```{r 00g_final-sp_annot, fig.height=1.7*6, fig.width=2*4}
# dev.new(width=12.5, height=12.5, noRStudioGD = TRUE)
# dev.new(height=1.7*6, width=2*4, noRStudioGD = TRUE)
DATA %>%
  plot_st_meta.fun(.,  
          assay="RNA",
          lab=T,
          feat = "sp_annot",
          zoom = "zoom",
          ncol = 4,
          annot_line = .1,
          annot_col = "black",
          img_alpha = 0,
          point_size = 0.5
        )
```

## Save seurat object
```{r save-SeuratObject}
##################################
# SAVE INTERMEDIATE SEURAT OJECT #
##################################
saveRDS(DATA, paste0(result_dir,"seuratObj_merged.RDS"))
# DATA <- readRDS(paste0(result_dir,"seuratObj_merged.RDS")) # seuratObj_merged_seurat_v5.RDS
```

### Session info
```{r}
sessionInfo()
```

