---
title: "hdWGCNA"
date: "`r format(Sys.time(), '%d %B, %Y')`"
format:
  html:
    embed-resources: true
    code-fold: show
params:
  fig.path: "`r paste0(params$fig.path)`" #./Figures/
editor_options: 
  chunk_output_type: console
---
## Heatmap of significant genes per cluster

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width     = 6.6929133858,
  fig.path      = params$fig.path,#"../Figures/",
  fig.align     = "center",
  message       = FALSE,
  warning       = FALSE,
  dev           = c("png"),
  dpi           = 300,
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename,
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
  }
  )
# resolve functions with same name across packages
select <- dplyr::select
#  setwd("~/work/Brolidens_work/Projects/Spatial_Microbiota/src")
```

```{r conda-env-setup}
# create new conda environment for R
# conda create -n hdWGCNA -c conda-forge r-base r-essentials

# activate conda environment
# conda activate hdWGCNA

# make sure the correct library path is set
.libPaths("/Users/vilkal/Applications/miniconda3/envs/hdWGCNA/lib/R/library")

# install BiocManager
install.packages("BiocManager")

# install Bioconductor core packages
BiocManager::install()

# install additional packages:
BiocManager::install(c("WGCNA", "igraph", "devtools", "GeneOverlap", "ggrepel", "UCell"))
devtools::install_github("NightingaleHealth/ggforestplot")

# alternatively, install Seurat v4
remotes::install_version("Seurat", "4.4.0", repos = c("https://satijalab.r-universe.dev", getOption("repos")))
# now install hdWGCNA
remotes::install_github('smorabit/hdWGCNA', ref='dev')
```


```{r background_job, eval=FALSE, include=FALSE}
source("../../bin/render_with_jobs.R")

# quarto
# render_html_with_job(out_dir = lab_dir)
# fs::file_move(path = file, new_path = paste0(lab_dir, file))

# currently using quarto for github and kniter for html due to source code option 
render_git_with_job(fig_path = "./Figures/07/")
system2(command = "sed", stdout = TRUE,
        args = c("-i", "''","-e", 's/src=\\"\\./src=\\"\\.\\./g',
                 paste0("./md_files/", basename("./07_figures.md"))))

# kniter
knit_html_with_job(out_dir = "../lab_book/figure_07", fig_path = "./Figures/07/")
```

### Load data and libraries
```{r Load_data}
##################
# LOAD LIBRARIES #
##################
.libPaths("/Users/vilkal/Applications/miniconda3/envs/hdWGCNA/lib/R/library")
library(tidyverse)
library(Seurat)
library(SeuratObject)
library(tidyseurat)
library(cowplot)
library(patchwork)
library(enrichR)
library(openxlsx)
library(readxl)
library(ComplexHeatmap)

# co-expression network analysis packages:
library(WGCNA)
library(hdWGCNA)

# enable parallel processing for network analysis (optional)
allowWGCNAThreads(nThreads = 8)

# using the cowplot theme for ggplot
theme_set(theme_cowplot())

# set random seed for reproducibility
set.seed(12345)

source("../bin/spatial_visualization.R")
source("../bin/plotting_functions.R")

#########
# PATHS #
#########
input_dir <- "../results/03_clustering_st_data/"
result_dir <- "../results/09_hdWGCNA/"
if( isFALSE(dir.exists(result_dir)) ) { dir.create(result_dir,recursive = TRUE) }
epi_clus <- "^5$|^6$|^7|^9" # non-filt

#############
# LOAD DATA #
#############
meta <- read_csv("../data/ST-samples_metadata.csv")
pseudo_DEGs <- readRDS("../results/06_DGE_condition_st_data/Pseudobulk_across_DEGs.RDS")
DEGs_table <- read_csv(paste0("../results/06_DGE_condition_st_data/","DGEs_condition_wilcox.0.7.csv"))
DATA <- readRDS(paste0("../results/03_clustering_st_data/","seuratObj_clustered.RDS"))
#DATA <- readRDS(paste0("/Users/vilkal/work/Brolidens_work/Projects/Spatial_Microbiota/results/07_sp_microbes/","seuratObj_microbes.RDS"))

# 16S data
dataset_names <- c("ASV_Luminal_raw_counts", # Tissue, Boston run 1 (108 samples)
                   "ASV_Tissue_raw_counts")  # Tissue, Boston run 2+1 (93 sample)
datasets <- map(dataset_names, 
  ~read_excel(paste0("../../data/", "Suppl.Tbl.01 Abundance, diversity, BCs and ASV counts.xlsx"), sheet = .x)) %>% 
  set_names(., dataset_names)

sample_id <- c("P020", "P045", "P050", "P057",
               "P008", "P031", "P080", "P044", "P026", "P105", 
               "P001", "P004", "P014", "P018", "P087", "P118",
               "P021", "P024", "P067", "P081", "P117" ) %>% set_names()
layers <- c("Superficial","Upper IM","Lower IM","Basal","1","4","0","3","2","9","10","11","12")
gr <- c('L1', 'L2', 'L3', 'L4') %>% set_names()
```

## select DEGs for WGCNA
```{r}
DEG_sig <- DEGs_table %>%
  filter(p_val_adj < 0.05) %>% 
  filter(!(grepl("^11$|$^12$", .$layers))) 

# the WGCNA was run with 3880 genes (all_Clus_4000DEGs) (it has 51 genes which are not significant and is missing 5 ACK genes)
# another run only included the WILK genes (3185) 
# Should run it one more time with All methods (WILK, PAIR and ACK) removing clus 11 and 12 (3771 genes)
genes <- unique(DEG_sig$gene)

# alternative with union of pseudobulk and wilcox 
WILK <- DEGs_table %>%
  filter(!(grepl("^11$|$^12$", .$layers))) %>%
  filter(p_val_adj < 0.05) %>% .$gene %>% unique()

PAIR <- pseudo_DEGs %>%
  select(pairwise) %>% unnest(cols = c(pairwise)) %>% filter(FDR < 0.05) %>% .$Genes %>% unique()

ACK <- pseudo_DEGs %>%
  select(across) %>% unnest(cols = c(across)) %>% filter(FDR < 0.05) %>% .$symbol %>% unique()

setdiff(PAIR, WILK)
intersect(intersect(PAIR, WILK), ACK)

genes <- c(PAIR, WILK, ACK) %>% unique()

```


## Construct metaspots with hdWGCNA

the group.by parameter slices the Seurat object to construct metaspots separately for each group
```{r Construct-metaspots-hdWGCNA}
# set idents
Idents(DATA) <- DATA$layers

# add image and spatial coordinates to metadata
coords <- map(sample_id, ~DATA@images[[.x]]@coordinates) %>% bind_rows() %>%
  select(row, col, imagerow, imagecol) %>% rownames_to_column(var = "barcodes")

DATA <- DATA %>% left_join(., coords, by=c( ".cell"="barcodes"))

# DATA %>% mutate(sp_annot = ifelse(.$layers == "Basal", "epi", .$sp_annot)) 

DATA <- SetupForWGCNA(
  DATA,
  features = genes,
  #fraction = 0.05,
  wgcna_name = "vis"
)

DATA <- MetaspotsByGroups(
  DATA,
  group.by = c("orig.ident"),
  ident.group = "orig.ident",
  assay = 'RNA'
)
DATA  <- NormalizeMetacells(DATA)
```

## Co-expression network analysis

```{r Co-expression-network}
# select specific region 
# Submucosa
# DATA  <- SetDatExpr(
#   DATA,
#   assay = "RNA",
#   group.by="layers",
#   group_name = c("1", "4", "3", "2", "10")
# )

# All spots
# set up the expression matrix, set group.by and group_name to NULL to include all spots
DATA  <- SetDatExpr(
  DATA,
  assay = "RNA",
  group.by=NULL,
  group_name = NULL
)

# test different soft power thresholds
DATA <- TestSoftPowers(DATA)
plot_list <- PlotSoftPowers(DATA)

p <- wrap_plots(plot_list, ncol=2)
ggsave(filename=paste0("./Figures/hdWGCNA/", "SoftPower_treshold.png"),p,  width = 5, height = 4, bg = "white")

# construct co-expression network:
DATA <- ConstructNetwork(
  DATA,
  soft_power = 9,
  tom_name='test',
  overwrite_tom=TRUE
)

# saveRDS(DATA, paste0(result_dir,"all_Clus_4000DEGs/","hdWGCNA_Seurat.RDS"))
# DATA <- readRDS(paste0(result_dir,"all_Clus_4000DEGs/","hdWGCNA_Seurat.RDS"))

# plot the dendrogram
PlotDendrogram(DATA, main='Spatial hdWGCNA dendrogram')

```

```{r get-gene-modules}
tom <- readRDS(paste0("./TOM/","test_TOM.rda"))
```

```{r change-module-colour}
# load MetBrewer color scheme pakckage
library(MetBrewer)

# get a table of just the module and it's unique color
mod_color_df <- GetModules(DATA) %>%
  dplyr::select(c(module, color)) %>%
  distinct %>% arrange(module)

# the number of unique modules (subtract 1 because the grey module stays grey):
n_mods <- nrow(mod_color_df) - 1

# using the "Signac" palette from metbrewer, selecting for the number of modules
new_colors <- paste0(met.brewer("Archambault", n=n_mods)) # "Archambault", "Signac", "Peru1"

# reset the module colors
DATA <- ResetModuleColors(DATA, c("#88a0dc","#f9d14a","#ed968c","#e78429"))
# DATA <- ResetModuleColors(DATA, c("#ed968c","#f9d14a","#88a0dc","#e78429"))

# save the dendrogram
png(paste0("./Figures/hdWGCNA/", "Spatial hdWGCNA dendrogram.png"), width = 10, height = 3, units = "in", res = 300)
PlotDendrogram(DATA, main='Spatial hdWGCNA dendrogram')
dev.off()
```

## Compute module eigengenes (MEs) and eigengene-based connectivities (kMEs) 
```{r Compute-MEs}
DATA <- ModuleEigengenes(DATA)
DATA <- ModuleConnectivity(DATA)

# reset the module names with the prefix “SM” (spatial modules)
DATA <- ResetModuleNames(DATA, new_name = "SM")

# saveRDS(DATA, paste0(result_dir,"hdWGCNA_3771DEGs_Seurat.RDS")) 
# DATA <- readRDS(paste0("../../results/09_hdWGCNA/all_Clus_4000DEGs/","hdWGCNA_Seurat.RDS"))

#write_csv(DATA@misc[["vis"]][["wgcna_modules"]], paste0(result_dir, "wgcna_all_Clus_modules.csv"))
write_csv(DATA@misc[["vis"]][["wgcna_modules"]], paste0(result_dir, "wgcna_3771DEGs_modules.csv"))
# modules <- read_csv(paste0("../../results/09_hdWGCNA/all_Clus_4000DEGs/", "wgcna_all_Clus_modules.csv"))
modules <- read_csv(paste0("../../results/09_hdWGCNA/", "wgcna_3771DEGs_modules.csv"))
```

```{r add-modules-to-seurat}
# get module eigengenes and gene-module assignment tables
MEs <-  DATA@misc[["vis"]][["MEs"]]# GetMEs(DATA) 
modules <- GetModules(DATA)
mods <- levels(modules$module); mods <- mods[mods != 'grey']

# add the MEs to the seurat metadata so we can plot it with Seurat functions
DATA@meta.data <- cbind(DATA@meta.data, MEs)

# add other metadata to seurat object:
DATA <- DATA %>% left_join(., select(meta, ID, Nugent="Nugent_Score_v3"), by=c( "orig.ident"="ID"))

mod_nest <- modules %>%
  nest(data = module)
mod_nest
```

## Data visualization

```{r Modules_across_groups_UMAP, fig.width=10, fig.height=10}
plot_filt.fun <- function(DATA, gr = "L1"){
  DAT <- filter(DATA, groups == gr)
  DAT@misc[["vis"]][["MEs"]] <- DATA@misc[["vis"]][["MEs"]][colnames(DAT),]
  plot_list <- ModuleFeaturePlot(DAT, reduction = "umapharmony", features = "MEs", title =F) 
  return(plot_list)
}

mod <-  c("SM1", "SM2", "SM3", "SM4") # , "SM5", "SM6"
mod <- map(mod, ~plot_genes.fun(DATA, 
               gene = .x, 
               scale = F,
               mins = -20, maxs = 20,
               diverging = T,
               col = rev(c("#B2182B","#D6604D","#F4A582","#FDDBC7","#F7F7F7","#D1E5F0","#92C5DE","#4393C3","#2166AC")),
               point_size = .5,
               red="umapharmony", 
               lable = TRUE))

(g <- map(seq_along(mod), ~mod[[.x]] + facet_wrap(~groups, ncol = 4)) %>% wrap_plots(., ncol=1) )
# ggsave(filename=paste0("./Figures/hdWGCNA/", "Modules_across_groups_UMAP.png"),g,  width = 10, height = 10, bg = "white")
```


```{r UMAP_module_groups, fig.width=15, fig.height=15}
# make a featureplot of hMEs for each module
plot_list <- DATA %>%
  ModuleFeaturePlot(., reduction = "umapharmony", features = "MEs") %>%
  wrap_plots(., ncol=4)

# for each microbiota group
(plots <- sort(unique(DATA$groups)) %>%
  set_names() %>%
  imap(., ~plot_filt.fun(DATA, .x)) %>% 
  flatten() %>% 
  wrap_plots(., ncol=4, guides = "collect")  %>%
  wrap_plots(plot_list, ., ncol=1, heights = c(.25,1)) )
# ggsave(filename=paste0("./Figures/hdWGCNA/", "UMAP_module_groups.png"),plots,  width = 15, height = 15, bg = "white")
```

```{r kME_ranked_genes, fig.width=11, fig.height=3}
# plot genes ranked by kME for each module
p <- PlotKMEs(DATA, ncol=5, text_size = 3 )
# ggsave(filename=paste0("./Figures/hdWGCNA/", "kME_ranked_genes.png"),p,  width = 11, height = 3, bg = "white")
```

```{r Group_contribution, fig.width=10, fig.height=3}
# relative expression level of each module
plot_list <- ModuleRadarPlot(
  arrange(DATA, layers),
  group.by = 'groups', combine = F, # ncol = 4, 
  #barcodes = seurat_obj@meta.data %>% subset(cell_type == 'INH') %>% rownames(),
  axis.label.size=4, group.line.width =  0.5,
  grid.label.size=4
) 
(p <- wrap_plots(plot_list, ncol=4) & theme(title = element_text(size=8)) )
# ggsave(filename=paste0("./Figures/hdWGCNA/", "Group_contribution.png"),p,  width = 10, height = 3, bg = "white")

```

```{r DotPlot_SM_representation, fig.width=7, fig.height=6}
# plot with Seurat's DotPlot function
mods <- unique(modules$module)[unique(modules$module) != 'grey']
p <- c('groups', 'layers', 'Nugent') %>%
  map(., ~DotPlot(DATA, features=rev(mods), group.by = .x, dot.min=0.1) )

# flip the x/y axes, rotate the axis labels, and change color scheme:
p <- map(p,~.x +
  coord_flip() +
  RotatedAxis() +
  scale_color_gradientn(colours = c('blue','grey95', 'red'), name = "Avg. Expression",
                       limits = c(-1.5, 2.5), oob = scales::squish,
                       values = scales::rescale(c(-1.5, 0, 2.5))) + 
    theme(legend.direction = "vertical", legend.box = "horizontal",
          plot.margin = unit(c(.1, -0, -1, -0), "lines")) + # t,r,b,l
    xlab('') + ylab('') + guides(col = guide_colourbar(barwidth = .5, barheight = 7 )) 
)

# combine plots
# dev.new(width=7, height=6, noRStudioGD = TRUE)
plot_grid(p[[1]], p[[2]]+theme(legend.position = "none"), p[[2]]+theme(legend.position = "none"), ncol = 1)

# save plots
#ggsave(filename=paste0("./Figures/hdWGCNA/", "dotplot_layers.png"),p[[2]],  width = 7, height = 2.5, bg = "white")
#ggsave(filename=paste0("./Figures/hdWGCNA/", "dotplot_groups.png"),p[[1]],  width = 4, height = 2, bg = "white")
#ggsave(filename=paste0("./Figures/hdWGCNA/", "dotplot_Nugent.png"),p[[3]],  width = 5, height = 2, bg = "white")

```


```{r MEs-on-tissue, fig.width=7, fig.height=7}
# dev.new(height=7, width=7, noRStudioGD = TRUE)
mods <- as.character(mods) %>% set_names()
p <- map(mods, ~plot_spatial.fun(
          #DATA@misc[["vis"]][["wgcna_metacell_obj"]],
          DATA, 
          assay="RNA",
          sp_annot = T,
          sampleid = sample_id,
          geneid = .x,
          lab = T,
          alpha = 1,
          ncol = 4,
          #max_val = 100,
          point_size = .15,
          save_space = F,
          img_alpha = 0,
          #colors = col_feat, # lightgray
          zoom = NULL ) )

ggsave(paste0("./Figures/hdWGCNA/","Modules_on_tissue", ".pdf"), height = 7, width = 7,
       gridExtra::marrangeGrob(grobs=p, ncol=1, nrow=1, top=NULL) )
```

```{r line-graph, fig.width=25, fig.height=5}
# pick out a few modules of interest here
modules_of_interest = c("SM1", "SM2", "SM3", "SM4")

# Pull out list of genes in that module
submod = DATA@misc[["vis"]][["wgcna_modules"]] %>%
  subset(module %in% modules_of_interest) 

# Get average expression across genes for each SM
m_obj <- DATA@misc[["vis"]][["datExpr"]][,submod$gene_name] %>%
  rownames_to_column(var = "barcode") %>%
  pivot_longer(-barcode) %>%
  #mutate(module = submod[.$name,]$colors) %>%
  left_join(., select(DATA, barcode=".cell", layers, ID="orig.ident", groups), by="barcode") %>%
  left_join(., select(GetModules(DATA), name=gene_name, module, color), by="name") %>%
  summarise(avg_exp = mean(value), .by = c("name","module", "layers", "ID", "groups")) %>%
  mutate(ID_ = paste0(.$ID, .$groups, .$layers))


col <- c("#88a0dc","#f9d14a","#ed968c","#e78429")
(p <- m_obj %>% 
  #filter(layers == "Basal") %>%
  #filter(avg_exp > 1) %>%
  arrange(layers) %>%
  arrange(groups) %>%
  
  mutate(ID_ = factor(.$ID_, levels = unique(.$ID_))) %>%
  ggplot(., aes(x=ID_, y=avg_exp, group=name)) +
  geom_line(aes(color = module),
            alpha = 0.2) +
  scale_color_manual(values = col) +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = 90)
  ) +
  #scale_color_identity() +
  #facet_wrap(~module + layers)
  facet_grid(rows = vars(module)) +
  labs(x = "treatment",
       y = "normalized expression") )

ggsave(filename=paste0("./Figures/hdWGCNA/", "Expression_lines_DEGs.png"),p,  width = 25, height = 5, bg = "white")
```


## visualize the co-expression network using UMAP

```{r co-expression-network-UMAP, fig.width=12, fig.height=10}
# perform UMAP embedding on the co-expression network
DATA <- RunModuleUMAP(
  DATA,
  n_hubs = 5,
  n_neighbors=15,
  min_dist=0.3,
  spread=1
)

# make the network plot
# can also return igraph object which can be manipulated by tidygraph
# dev.new(width=12, height=10, noRStudioGD = TRUE) 
pdf(paste0("./Figures/hdWGCNA/", "WGCNA_UMAP.pdf"),  width = 12, height = 12)
# Margins area
par(oma=c(0,0,0,0)) #bltr
par(mar=c(0,0,0,2))
ModuleUMAPPlot(
  DATA,
  edge.alpha=0.5,
  sample_edges=TRUE,
  keep_grey_edges=FALSE,
  vertex.label.cex = 0.7,
  return_graph = FALSE,
  edge_prop=0.075, 
  label_hubs=7 
) 
dev.off()
```


```{r trait-correlation, eval=FALSE}
group1 <- DATA %>% filter(layers == "1" & groups == "L1") %>% colnames
group2 <- DATA %>% filter(layers == "1" & groups == "L4") %>% colnames
group2 <- DATA %>% filter(layers == "Superficial" & groups == "L3") %>% colnames

DMEs <- FindDMEs(
  DATA,
  barcodes1 = group1,
  barcodes2 = group2,
  test.use='wilcox'
)

head(DMEs)

PlotDMEsLollipop(
  DATA, 
  DMEs, 
  wgcna_name='vis', 
  pvalue = "p_val_adj"
)

PlotDMEsVolcano(
  DATA,
  DMEs,
  wgcna_name = 'vis'
)
```

## Individual module network plots
```{r Hubb-gene-networks}
ModuleNetworkPlot(
  DATA,
  outdir = './Figures/hdWGCNA/ModuleNetworks'
)

# all modules
pdf(paste0("./Figures/hdWGCNA/", "Hub_network_all.pdf"), width = 12, height = 15)
HubGeneNetworkPlot(
  DATA,
  n_hubs = 7, n_other=20,
  edge_prop = 0.75,
  mods = 'all'
)
dev.off()

# single module
mod <-  c("SM1", "SM2", "SM3", "SM4") 
Hub_network.fun <- function(module, bg="white"){
  
  HubGeneNetworkPlot(
    DATA,
    n_hubs = 15, n_other=30,
    hub.vertex.size = 6,
    vertex.label.cex = 0.3,
    edge_prop = 0.75,
    mods = module,
    wgcna_name = "vis"
  )

}
pdf(paste0("./Figures/hdWGCNA/", "Hub_network_15.pdf"), 
    width = 8, height = 5,  bg = "transparent") 
map(mod, ~Hub_network.fun(.x, bg = "transparent"))
dev.off()
```

```{r enrichR}
# enrichr databases to test
dbs <- c('GO_Biological_Process_2021','KEGG_2021_Human','Transcription_Factor_PPIs')

# perform enrichment tests
DATA <- RunEnrichr( #map(dbs, ~
  DATA,
  dbs=dbs, # character vector of enrichr databases to test
  max_genes = Inf # number of genes per module to test. use max_genes = Inf to choose all genes!
)

# retrieve the output table
enrich_df <- GetEnrichrTable(DATA) %>%
  filter(Adjusted.P.value < 0.05) %>% 
  split(~db)

enrich_df %>%
  map(., ~split(.x, ~module)) %>%
  imap(., ~write.xlsx(.x, paste0(result_dir,"New_3771DEGs/", "Enrichment_",.y,".xlsx")) )

# saveRDS(enrich_df, paste0("../../results/09_hdWGCNA/all_Clus_4000DEGs/", "Enrichment.RDS"))
# enrich_df <- readRDS(paste0("../../results/09_hdWGCNA/all_Clus_4000DEGs/", "Enrichment.RDS"))
# enrich_df <- read.xlsx(paste0("../../results/09_hdWGCNA/all_Clus_4000DEGs/", "Enrichment_all_Clus.xlsx"))

# make GO term plots:
EnrichrBarPlot(
  DATA,
  outdir = paste0("./Figures/hdWGCNA/","enrichr_plots"), # name of output directory
  n_terms = 10, # number of enriched terms to show (sometimes more show if there are ties!!!)
  plot_size = c(5,7), # width, height of the output .pdfs
  logscale=TRUE # do you want to show the enrichment as a log scale?
)

# ggsave(filename=paste0("./Figures/hdWGCNA/", "enrichment_DEGs.pdf"), width = 6, height = 4)
```

```{r Enrichment-plot, fig.width=12, fig.height=4}
#######################
# ENRICHMENT BARPLOT #
#######################
overlap.fun <- function(string){
  l <- str_split(string, pattern ="/")
  l <- map_dbl(l, ~as.numeric(.x[1])/as.numeric(.x[2]) )
  return(l)}

# str_match("cytoplasmic translation (GO:0002181)", "^(.+?)\\s\\((.+)\\)$")[2]
GeneRatio_plot.fun <- function(enrich_df, txt_size = 15, nr_path=3,
                               col=c("#ed968c","#f9d14a","#88a0dc","#e78429")){
  dot_df <- enrich_df %>%  # dot_df <- enrich_df$GO_Biological_Process_2021 %>%
    {if(grepl("GO",.$Term[[1]])){mutate(., "Term" = str_match(.$Term, "^(.+?)\\s\\((.+)\\)$")[,2], 
           "GOid" = str_match(.$Term, "^(.+?)\\s\\((.+)\\)$")[,3] )}else .} %>%
    filter(Adjusted.P.value < 0.05) %>%
    mutate("-log10(P-value)" = -log10(P.value)) %>%
    mutate(GeneRatio = overlap.fun(.$Overlap)*100) 
  
  dot_df <- dot_df %>%
    group_by(module) %>% 
    top_n(., -nr_path, Adjusted.P.value) 
  
  p <- ggplot(dot_df, aes(x = `-log10(P-value)`, y = fct_reorder(Term, `-log10(P-value)`), fill = module, col = module)) +
    geom_col(width = .05, show.legend = F) +
    geom_point(aes(size = GeneRatio)) + theme_classic() + 
    scale_fill_manual(values = col, aesthetics = c("fill", "colour")) +
    
    facet_wrap(~module, scales = 'free', ncol = 1) +
    #scale_x_continuous(expand = c(0, 1.5)) +
    coord_cartesian(clip = F) +
    scale_x_continuous(limits = function(x){c(0, +max(0.1, x))}) +
    scale_size_continuous(breaks = c(10, 50, 80)) +
    theme(axis.title.y = element_blank(),
          legend.position = "none",
          strip.text.x = element_text(hjust = 0.1, margin=margin(l=0)),
          strip.background = element_blank(),
          panel.spacing = unit(0, "cm"),
          panel.border = element_blank())
  return(p)
}


p1 <- GeneRatio_plot.fun(enrich_df$Transcription_Factor_PPIs) 
p2 <- GeneRatio_plot.fun(enrich_df$GO_Biological_Process_2021) 
p3 <- GeneRatio_plot.fun(enrich_df$KEGG_2021_Human) 

# dev.new(width=12, height=4, noRStudioGD = TRUE) 
(plot <- wrap_plots(p1,p2,p3, ncol = 3 ) )

# ggsave(paste0("./Figures/hdWGCNA/", "Enrichment.png"),plot,  width = 11, height = 3, bg = "white")
```

```{r barplot-function}
#####################################################
# OVERLAPING GENES BETWEEN SPATIAL MODULES AND DEGs #
#####################################################
# Get all combinations of layers
overlap_barplot.fun <- function(DEGs){
  DEGs_list <- map(DEGs, ~set_names(.x$gene, .x$Regulation)) #map(DEGs, ~pull(.x, "gene"))
  t <- c(DEGs_list, module_genes[2:5]) %>% 
  tibble(genes=., layers=names(.))
  
  DEGs_list <- rep(t$layers[1:11], 4)
  SM <- c(rep("SM1", 11), rep("SM2", 11), rep("SM3", 11), rep("SM4", 11))
  n <- paste0(SM , "_", DEGs_list)
  
  # Find intersections for each combination
  intersections <- function(df, comb) {
    genes_comb <- df$genes[df$layers %in% comb]
    Reduce(intersect, genes_comb)
  }
  int <- map2(DEGs_list, SM, ~intersections(t, c(.x, .y))) %>% set_names(., n)
  
  # Combine combinations and intersections into a data frame
  intersections_df <- tibble(name = names(int), intersections = int, SM = SM, layers = DEGs_list) %>%
    mutate(n = map_int(intersections, ~length(.x)))
  
  # Print the intersections
  knitr::kable(intersections_df, caption = "All overlaping genes for all combinations")
  
  col <- c("#E41A1C","#FF7F00","#C77CFF","#984EA3","#00BFC4","#00A9FF","#377EB8",
                "#CD9600","#7CAE00","#e0e067","#FFFF33","#FF61CC","#FF9DA7","#999999","#A65628")
  col <- c("#569EFF","#FF706A")
  
  plot <- intersections_df %>%
    mutate(layers = factor(.$layers, levels=unique(.$layers))) %>%
    unnest(intersections) %>%
    mutate(comb = DEGs[[1]][["comb"]][1]) %>%
    left_join(., select(DEG_list[[.$comb[1]]], gene, Regulation, avg_log2FC, layers), by=c("intersections"="gene", "layers")) %>%
    {. ->> l} %>%
    ggplot(., aes( x=layers, fill=Regulation)) +
      geom_bar(stat="count") + #ylim(0,800)+
      scale_fill_manual(values = col) + theme_classic() +
    theme(axis.text.x = element_text(angle = 30, hjust = 1),
          axis.title = element_blank()) +
    #facet_wrap(~SM, ncol = 4)
    facet_grid(cols = vars(SM), rows = vars(comb))
  
  return(tibble(plot=list(plot), genes= list(l)))
}
```


```{r DEG-module-overlap, fig.width=14, fig.height=12}
DEG_list <- DEGs_table %>%
  filter(p_val_adj < 0.05) %>% 
  filter(!(grepl("^11$|$^12$", .$layers))) %>%
  mutate(layers = factor(.$layers, levels=unique(.$layers))) %>%
  {. ->> DEG_sig} %>%
  split(~comb) 

DEG_genes <- DEG_list %>% map(., ~split(.x, ~layers)) 
module_genes <- GetModules(DATA) %>% split(~module) %>% map(., ~pull(.x, "gene_name"))

###########
# BARPLOT #
###########
overlap <- names(DEG_genes) %>%
  set_names() %>%
  map(., ~overlap_barplot.fun(DEG_genes[[.x]])) %>%
  bind_rows(., .id = "comb") 
  
# dev.new(width=14, height=12, noRStudioGD = TRUE) 
(p <- wrap_plots(overlap$plot, ncol = 1))

# ggsave(paste0("./Figures/hdWGCNA/","barchart_WILK_DEGs.png"),p, width = 14, height = 12)

```


